Placeholder

### 2021-02-22 Paper_Histograms.Rmd
Updated caption for main retro plot concerning self-defined/non-binary pt's for each cohort

@@

grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, 
          nrow = 2,
          #heights=c(1, 1.2),
          bottom = textGrob("Non-binary/Self-defined: GLAD/EDGI (243); NBR (39); RAMP (92)", x = 1,
                            hjust = 1,
                            gp = gpar(fontface = 3L, fontsize = 9)))

>>>>

```{r See non-binary/self-defined pt's by sample for caption}

dat.retro %>% 
  group_by(Sample_plot, Gender_collapsed) %>% 
  summarise(n = n())

@@

grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, 
          nrow = 2,
          #heights=c(1, 1.2),
          bottom = textGrob("Non-binary/Self-defined: GLAD (247); NBR/EDGI (41); RAMP (92)", x = 1,
                            hjust = 1,
                            gp = gpar(fontface = 3L, fontsize = 9)))
